### 2019-03-29 thesis-template/msc-thesis.tex
update

\vspace*{100pt}
\noindent
\emph{dt.:}
Ich versichere, dass ich diese Master-Arbeit selbstständig verfasst und nur die angegebenen
Quellen und Hilfsmittel verwendet habe und die Grundsätze und
Empfehlungen ``Verantwortung in der Wissenschaft'' der Universität Heidelberg beachtet wurden. 
\bigskip
\\
\emph{eng.:}
I hereby declare/assure, that I drafted this thesis independently and only used the labeled/denoted/indicated sources/references, materials and that the conventions/principles and recommendations ``Verantwortung in der Wissenschaft'' of the Heidelberg University have been regarded/observed. 
\vspace*{50pt}
\noindent

>>>>

\vspace*{100pt}
\noindent
\emph{dt.:}
Ich versichere, dass ich diese Master-Arbeit selbstständig verfasst und nur die angegebenen
Quellen und Hilfsmittel verwendet habe und die Grundsätze und
Empfehlungen ``Verantwortung in der Wissenschaft'' der Universität Heidelberg beachtet wurden. 
\bigskip
\\
\emph{eng.:}
I hereby declare/assure, that I drafted this thesis independently and only used the sources and materials labeled as references and that the conventions/principles and recommendations ``Verantwortung in der Wissenschaft'' of the Heidelberg University have been regarded/observed. 
\vspace*{50pt}
\noindent
